% Handout: asking clinical questions
% Author: Thomas Klee
% 22 Jan 2017

% Preamble --------------------------------------------------------

\documentclass[a4paper]{article}
\usepackage[]{fullpage}
\usepackage[latin1]{inputenc}
\usepackage{multicol}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = black]{hyperref} 
\usepackage[natbibapa]{apacite}
\usepackage{amsmath}
\usepackage{textcomp}

% Course title etc ---------------------------------------------------

\title{Examples of Clinical Questions\footnote{Not expressed in PICO format.}}
\author{Thomas Klee}
\date{Evidence-Based Practice in Speech-Language Therapy (SHSC 2033)}

% Document ---------------------------------------------------------------

\begin{document}

\maketitle

\begin{enumerate}

\item Does using sign language with normal-hearing babies and toddlers accelerate children's language development? \\
\\
   \emph{Why ask this question?} Baby Signs programmes are offered to parents of young children all over the world. The notice board in my GP's waiting room advertises such a group and at least one local ST practice offers this as a form of intervention. And a website claims that ``More than two decades of Baby Signs\textsuperscript{\textregistered{}} research has shown\ldots proven benefits [in] different areas of a child's development." (retrieved 20 January 2017) \url{http://www.babysignstoo.com/information/benefits}
		
\item Is phonological awareness therapy more effective, or more efficient, than other intervention approaches in treating children with speech sound disorders? \\
\\
   \emph{Why ask this question?} This is a relatively new approach to intervention that a lot of people are talking about and I want to know whether it's worth using in my practice.
		
\item Is the \emph{Fast ForWord} computer program an effective intervention in treating children with language impairment? \\
\\
   \emph{Why ask this question?} The children I work with love computer games and this seems like an ideal way of getting children to attend to 	intervention tasks while having fun.
	
\item How accurate is the Renfrew Action Picture Test for diagnosing developmental language disorders in children? \\
\\
   \emph{Why ask this question?} The STs on my clinical placement use this test and I want to find out more about it, especially since I don't recall it being discussed in class.
	
\item How effective is the McGuire Programme for treating adults who stammer? \\
\\
   \emph{Why ask this question?} One of my clients asked me what I thought of this approach to intervention after reading what Gareth Gates had to say about it in the Metro newspaper.
	
\item Is Facilitated Communication an effective form of AAC in improving the communication ability of people with severe motor disabilities? \\
\\
   \emph{Why ask this question?} I'm frustrated with the approach I've been using and came across a website claiming that it provides ``an effective means of expression for some individuals with labels of autism and other developmental disabilities" (\url{http://autism.about.com/od/alternativetreatmens/a/FC.htm}; retrieved 20 January 2017)

\end{enumerate}

\end{document}