% Handout: Cochrane tables comparison
% Given to students at last class meeting
% Author: Thomas Klee
% 10 Apr 2017

% Preamble --------------------------------------------------------

\documentclass[a4paper]{article}
\usepackage[]{fullpage}
\usepackage[latin1]{inputenc}
\usepackage{multicol}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = black]{hyperref} 
\usepackage[natbibapa]{apacite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{caption}

% Course title etc ---------------------------------------------------

\title{Cochrane Table Summarising Study Details}
\author{Thomas Klee  \\ The University of Hong Kong}
\date{Evidence-Based Practice in Speech-Language Therapy (SHSC 2033)}

% Document ---------------------------------------------------------------

\begin{document}

\maketitle

Written Assignment 2 asks you to include a list of the ``included studies in your review, summarised in a table based on the Cochrane reporting framework" (Course Syllabus, p. 4). Examples of Cochrane table headings used in two studies are provided below. As can be seen, each study table contains slightly different information. The paper by \citet{Meinusch2011} contains an extra row stating the research question being asked, whereas the paper by \citet{Law2003b} does not. Here's how the two Cochrane tables compare, using the terms the authors used:

\begin{center}
\begin{tabular}{l l}
\toprule
\citet[p. 26]{Law2003b} & \citet[Appendix]{Meinusch2011} \\
\midrule
Author (Date)	& Author (Date) \\
Methods	& Study Design \\
---		& Question \\
Participants	& Subjects \\
Interventions	& Intervention \\
Outcomes	& Outcomes \\
Notes		& Notes \\
Risk of Bias	& Risk of Bias \\
\bottomrule
\end{tabular}
\end{center}

Your assignment instructions indicate using 7 rows, as were used by \citet{Law2003b}, but if you want to add another for the research question, that's fine. The ``Risk of Bias" row can be used to list \emph{all} suspected sources of bias in the study.

The Outcomes row should list the main outcome measure(s) of interest. The result associated with each outcome (e.g., ES) should either be listed in the table or in the text, but be sure to include in one of these places. 

\bibliographystyle{apacite}
\bibliography{/Users/thomasklee/Documents/Bibtex/library}

\end{document}